### 2020-08-06 reports/article.tex
bar2

\subsection*{Refining LULC classes based on tree cover and building density}
\label{sec:refin-lulc-class}

@@

@@

>>>>

\subsubsection*{Refining LULC classes based on tree cover and building density}
\label{sec:refin-lulc-class}

@@

\subsection*{Relationships between the spatial pattern of tree canopy on urban heat mitigation}

In order to explore the relationships between the \cite{rey2010pysal}

@@

\subsection*{Relationship between }
